\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{xcolor}

\title{Plum / Stonefruit Race}
\author{Dante Buhl}


\DeclareMathOperator{\cond}{cond}
\DeclareMathOperator{\vecspan}{span}
\DeclareMathOperator{\sign}{sign}

\begin{document}

\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\bmp}[1]{\begin{minipage}{#1\textwidth}}
\newcommand{\emp}{\end{minipage}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\I}{\mathrm{I}}
\newcommand{\K}{\bs{\mathrm{K}}}
\newcommand{\m}{\bs{\mu}_*}
\newcommand{\s}{\bs{\Sigma}_*}
\newcommand{\dt}{\Delta t}
\newcommand{\tr}[1]{\text{Tr}(#1)}
\newcommand{\Tr}[1]{\text{Tr}(#1)}

\maketitle



\begin{itemize}

    \item \textbf{Ability Score Increase} Your intelligence score increases by 2
    
    \item \textbf{Age} Stonefruits mature at the same rate as humans, and live to be around 350 years old. At the end of their life, they can plant themselves and become trees. 
 
    \item \textbf{Alignment} Plum Stonefruits are typically good, but stonefruits can be of any alignment. 

    \item \textbf{Size} Small
 
    \item \textbf{Speed} Walking 25 feet
 
    \item \textbf{Darkvision} Accustomed to the 

    \item \textbf{Gnome Cunning}

    \item \textbf{Stonefruit Stun} Stonefruits have an innate ability to eject a seed pit and have an effect in a small area (radius 10 ft)  around the pit. The effect of this ability is determined by which stonefruit it is used by. Plums gain access to 3 enchantment spells. The seed pit dispersed by Plums give off a sweet aroma. At level 1, the seed pit has the same effect as the Friends Cantrip. At level 3, the seed pit can have the same effect as Charm Person spell. At level 5, the seed pit can have the same effect as the Calm Emotions spell. If the seed pit can have multiple effects, the stonefruit determines which effect it has, but can chose only one effect per use. If the spell effect used would normally make the target aware of its effect after the effect ended, this no longer happens. Stonefruit can use this ability once per long rest.
    
    \item \textbf{Languages} 
    
\end{itemize}

\end{document}
